---
title: "PK object batch mode trial"
author: "Gilberto Padilla Mercado"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)

library(tidyverse, quietly = TRUE)
devtools::load_all() # Loads the invivopkfit package in feature/pkS3obj_facet branch
tidyverse_conflicts()
```

## Working with one DTXSID + Species combination

The first step is understanding how to work with a single DTXSID + Species combination.
Once we know how to do this, it will be easier to apply it to (potentially)
a list of these objects in a vectorized fashion.
Here I subset the `cvt` object and use that as my working data.

```{r data_loading}
# There are 103 unique chemicals in this object
cvt %>% pull(chemicals_analyzed.dsstox_substance_id) %>%
  unique() %>%
  length()

my_predata <- subset(cvt,
                     chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                                   "DTXSID2021731",
                                                                   "DTXSID5032600"))
```

Next, I want to follow the steps required for the particular analysis I would like.
In this instance, I set the optimizer to "L-BFGS-B" and dose-normalize the output.
I do not scale the time or log-transform the concentration values.
Since I would like to do a "Pooled" analysis,
I set the `error_group = vars(Chemical, Species)`.

```{r single_fit}
my_pk <- pk(data = my_predata) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species, Reference)) 

my_pk <- do_preprocess(my_pk)

my_pk <- do_data_info(my_pk) 
# summarizes error (Returning more or less than 1 row per summarize)

my_pk <- do_prefit(my_pk)

my_pk <- do_fit(my_pk)
```

Batch mode works! Now, I have updated the `coef`, `predict`, `rmse`, and `residuals`
methods.

```{r after_method_update}
# Changed pk_methods coef() and predict() to those above
# Ran the following after making the pk object:
devtools::load_all()

my_coefs_update <- coef(my_pk)
my_pred_update <- predict(my_pk,
                          exclude = TRUE, # add the "exclude" column to output
                          use_scale_conc = TRUE)

predict(my_pk,
        exclude = TRUE, # add the "exclude" column to output
        use_scale_conc = TRUE)


my_pred2 <- predict(my_pk,
                    newdata = data.frame(Chemical = "DTXSID2021731",
                                         Species = "rat",
                                         Route = "iv",
                                         Media = "plasma",
                                         Dose = 20,
                                         Time = 1.6,
                                         Time.Units = "hours"),
                    exclude = FALSE,
                    use_scale_conc = FALSE)

rmse(my_pk) %>% View("RMSE_test")
residuals(my_pk) %>% View("Residuals_test")

```


```{r plotting_method}


plot(my_pk, use_scale_conc = TRUE,
     print_out = TRUE, log10_C = FALSE)

my_plot <- plot(my_pk, use_scale_conc = TRUE)

# This is printable into a one file, multipage pdf
pdf(file = "C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Code Notes/plotMethod_freeY.pdf",
    width = 10,
    height = 8)
plot(my_pk, use_scale_conc = TRUE,
     print_out = TRUE)
dev.off()

png(file = "C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Code Notes/examplePlot.png",
    width = 8,
    height = 6,
    units = "in",
    res = 150,
    type = "cairo",
    antialias = "none")
plot(my_pk, use_scale_conc = TRUE,
     method = "L-BFGS-B",
     print_out = TRUE)[[3]]
dev.off()


```



```{r remaining_methods}
# coef_sd
# logLik.pk
# get_tkstats()
devtools::load_all()
get_tkstats(my_pk) %>% head()
get_tkstats(my_pk) %>% View("TK_test")
my_tkstats <- get_tkstats(my_pk)

# For the July 5th version where it returns a nested dataframe
# 
my_tkstats %>%
  reframe(tkstats_df = purrr::map(c_data,
                                  \(x) {
                                    x %>%
                                      dplyr::rowwise() %>%
                                      dplyr::mutate(
                                        TKstats = sapply(
                                          coefs_vector,
                                          FUN = tk_fun,
                                          route = Route,
                                          medium = Media,
                                          dose = Dose,
                                          time_unit = Time.Units,
                                          conc_unit = Conc.Units,
                                          vol_unit = "L",
                                          simplify = FALSE,
                                          USE.NAMES = TRUE
                                        )
                                      ) %>%
                                      dplyr::ungroup()
                                  })) -> my_tkstats




my_tkstats %>% unnest(cols = c(tkstats_df)) -> my_tkstats

my_tkstats %>% mutate(TKstats_wide  = map(TKstats,
                                     \(x) {
                                       dplyr::select(x, -param_units) %>%
                                         tidyr::pivot_wider(names_from = param_name,
                                                     values_from = param_value)
                                     })) %>%
  unnest(cols = c(TKstats_wide)) %>% View()

```



