---
title: "Clearance Project - 3 - TKstats"
author: "Gilberto Padilla Mercado"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r library-loading}
today <- format(Sys.Date(), "%d%b%Y")
devtools::load_all()
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(ctxR)
library(ggdist)
library(patchwork)
library(httk)
load_dawson2021()

```


```{r data-loading}
# Note that you should run ...-1-Data.Rmd before this
# RCdata/ is a directory that is not tracked by git because it contains
# large files 
this_pk <- readRDS("data-raw/plasma_CvTfits.rds")
load("data-raw/chem_lists.RData")
load("data-raw/plasma_CvTfits_data.RData")
load("data-raw/rat_pars_human.RData")
load("data-raw/rat_pars_rat.RData")
all_chem_properties <- readRDS("data-raw/RCdata/ctxR_3comp2_cheminfo.rds")
full_pk <- readRDS("data-raw/all_cvt_pk.rds")
full_tkstats <- get_tkstats(full_pk)
```

## Species-specific differences in fraction unbound and intrinsic clearance

We first want to establish that there is a difference between human and rat
parameterization. Because one of our `param_df`s is only rat and the other has
substituted human parameters (scaled to a rat).

```{r rat_human_diff_fupClint}
fup_rh <- rpr_param_df %>% 
  distinct(Chemical, MW,
           Clint, Funbound.plasma) %>% 
  rename_with(\(x) {paste0(x, "_rat")},
              .cols = c(Clint, Funbound.plasma)) %>%
  left_join(
    rph_param_df %>%
      distinct(Chemical, MW,
               Clint, Funbound.plasma) %>% 
      rename_with(\(x) {paste0(x, "_human")},
                  .cols = c(Clint, Funbound.plasma))
    )

species_fup_pl <- fup_rh %>%
  ggplot(aes(
    Funbound.plasma_human,
    Funbound.plasma_rat
  )) +
  geom_abline(slope = 1) +
  geom_point() +
  geom_smooth(method = "lm", linetype = "dashed",
              color = "forestgreen") +
  labs(title = expression(f[up]),
       x = "Human", y = "Rat") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5)) +
  coord_equal(xlim = c(0,1), ylim = c(0,1), expand = TRUE)

fup_pl <- ggExtra::ggMarginal(
  species_fup_pl,
  type = "histogram",
  binwidth = 0.025,
  fill = "white"
)

lm(
  Funbound.plasma_rat ~ Funbound.plasma_human,
  data = fup_rh
)

cor.test(fup_rh$Funbound.plasma_human,
            fup_rh$Funbound.plasma_rat)


## Clint
species_clint_pl <- subset(
  fup_rh, Clint_human < 500, Clint_rat < 500
) %>%
  ggplot(aes(
    Clint_human,
    Clint_rat
  )) +
  geom_abline(slope = 1) +
  geom_abline(slope = 1, intercept = c(-50,50), linetype = "longdash") +
  geom_point() +
  # geom_smooth(method = "lm", linetype = "dashed", color = "forestgreen") +
  labs(title = expression(CL[int]),
       x = "Human", y = "Rat") +
  coord_equal(xlim = c(0,500), ylim = c(0,500)) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5,vjust = -1))

clint_pl <- ggExtra::ggMarginal(
  species_clint_pl,
  type = "histogram",
  fill = "white"
)

lm(
  Clint_rat ~ Clint_human,
  data = fup_rh
)

cor.test(fup_rh$Clint_human,
            fup_rh$Clint_rat)

# Both plots
species_fup_pl + species_clint_pl +
  plot_layout(axis_titles = "collect")

ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "RestrictiveClearance_Analysis/",
                         "Rat_Human_Interspecies_FupCLint_compare.png"),
       height = 3, width = 6)


# Get the "close" estimates (+/-50)
close_clint <- fup_rh %>%
  filter(between(Clint_rat, Clint_human - 50, Clint_human + 50)) %>%
  pull(Chemical)

rph_rmsle <- rph_httk_preds %>%
  mutate(fupSpecies = "human",
         rest_sqerror = (log10(httk_Preds_restrictive) - log10(Conc))^2,
         nonrest_sqerror = (log10(httk_Preds_nonrestrictive) - log10(Conc))^2) %>%
  group_by(
    Chemical, Species, fupSpecies
  ) %>%
  summarize(rest_rmsle = sqrt(sum(rest_sqerror)/n()),
            nonrest_rmsle = sqrt(sum(nonrest_sqerror)/n())
  ) %>%
  ungroup()

rpr_rmsle <- rpr_httk_preds %>%
  mutate(fupSpecies = "rat",
        rest_sqerror = (log10(httk_Preds_restrictive) - log10(Conc))^2,
         nonrest_sqerror = (log10(httk_Preds_nonrestrictive) - log10(Conc))^2) %>%
  group_by(
    Chemical, Species, fupSpecies
  ) %>%
  summarize(rest_rmsle = sqrt(sum(rest_sqerror)/n()),
            nonrest_rmsle = sqrt(sum(nonrest_sqerror)/n())
  ) %>%
  ungroup()

bind_rows(rpr_rmsle, rph_rmsle) %>%
  mutate(close_clint = ifelse(Chemical %in% close_clint,
                              "|CLint| within 50", "|CLint| > 50")
  ) %>% 
  filter(Chemical %in% unique(rpr_rmsle$Chemical)) %>%
  ggplot(aes(nonrest_rmsle, rest_rmsle)) +
  geom_abline(slope = 1, color = "blue") +
  geom_point(aes(color = fupSpecies), shape = 21) +
  scale_color_manual(values = c("green4", "magenta3")) +
  facet_grid(cols = vars(close_clint)) +
  geom_line(aes(group = paste0(Chemical)),
            alpha = 0.4) +
  labs(x = "Nonrestrictive RMSLE", y = "Restrictive RMSLE") +
  theme_bw() +
  coord_equal()
  

interspecies_rmsle_trends <- bind_rows(rpr_rmsle, rph_rmsle) %>%
  mutate(
    close_clint = ifelse(Chemical %in% close_clint,
                         "|\U0394 CLint| within 50", "|\U0394 CLint| > 50")
  ) %>% 
  filter(Chemical %in% unique(rpr_rmsle$Chemical)) %>% 
  pivot_longer(cols = contains("_rmsle"),
               names_to = "clearance_type",
               values_to = "RMSLE") %>%
  pivot_wider(names_from = fupSpecies,
              values_from = RMSLE) %>%
  mutate(norm_diff = (human - rat)/rat)

irt_pl <- interspecies_rmsle_trends %>%
  filter(!is.na(norm_diff)) %>% 
  ggplot(aes(x = forcats::fct_reorder(Chemical, norm_diff, mean),
             y = norm_diff,
             fill = clearance_type)) +
  geom_col(
    width = 0.6,
    # fill = "grey5", 
    position = position_dodge(),
    color = NA
    ) +
  labs(
    x = "Chemical",
    y = "Fold Change RMSLE\nHuman more accurate <<     >> Rat more accurate"
  ) +
  scale_fill_manual(values = c("grey20", "seagreen"),
                    breaks = c("nonrest_rmsle", "rest_rmsle"),
                    labels = c("Nonrestrictive", "Restrictive"),
                    name = "Clearance") +
  geom_hline(yintercept = 0) +
  theme_minimal() + 
  facet_grid(cols = vars(close_clint),
             # rows = vars(clearance_type),
             space = "free_x", scales = "free_x") +
  theme(axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(color = "grey5"),
        panel.background = element_rect(color = "grey5"),
        axis.title = element_text(size = 10),
        legend.position = "bottom")

species_clint_pl + irt_pl +
  plot_layout(widths = c(5,8))

ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "RestrictiveClearance_Analysis/",
                         "Rat_Human_Interspecies_RMSLE_trends.png"),
       height = 5, width = 7,
       bg = "white")
```

From this we notice that CLint specifically can have drastic differences which
we want to explore. We also glean that there are potential drastic improvements
in model accuracy. We next want to compare how a changing human CLint towards rat
CLint by 1% steps changes RMSE.

```{r}
combo_clint <- rpr_param_df %>%
  select(Chemical, rCLint = CLint) %>% 
  left_join(rph_param_df %>%
              select(Chemical, hCLint = CLint)) %>%
  mutate(hclint_1p = (1/10)*hCLint, 
         direction = sign(hCLint - rCLint)) %>%
  mutate(Nstep = ifelse(direction == 0, 
                        0, abs(hCLint - rCLint) %/% hclint_1p))

combo_clint %>%
  left_join(interspecies_rmsle_trends) %>%
  ggplot(aes(Nstep, norm_diff)) +
  geom_point() +
  scale_x_log10() +
  theme_bw()
```

Next I want to categorize each chemical based on putative hepatic extraction ratio.
This is calculated as:

$$
E_H = \frac{f_{up}\cdot CL_{int}}{Q_{hep} + f_{up}\cdot CL_{int}}
$$
```{r extraction_ratio}
rat_er <- rpr_param_df %>%
  group_by(Chemical) %>%
  reframe(fupClint = (Funbound.plasma * Clint),
          Qhep = (Qcardiacc*Qliverf)) %>%
  mutate(extraction_ratio = fupClint/(Qhep + fupClint),
         clearance_type_by_er = case_when(
           extraction_ratio >= 0.7 ~ "Nonrestrictive",
           extraction_ratio < 0.3 ~ "Restrictive",
           between(extraction_ratio, 0.3, 0.7) ~ "Ambiguous"
         )
  )

human_er <- rph_param_df %>%
  group_by(Chemical) %>%
  reframe(fupClint = (Funbound.plasma * Clint),
          Qhep = (Qcardiacc*Qliverf)) %>%
  mutate(extraction_ratio = fupClint/(Qhep + fupClint),
         clearance_type_by_er = case_when(
           extraction_ratio >= 0.7 ~ "Nonrestrictive",
           extraction_ratio < 0.3 ~ "Restrictive",
           between(extraction_ratio, 0.3, 0.7) ~ "Ambiguous"
         )
  ) 

combo_pretable <- inner_join(
  rat_er %>% select(Chemical,
                    "rat_er" = extraction_ratio, 
                    "rat_cl" = clearance_type_by_er),
  human_er %>% select(Chemical,
                    "human_er" = extraction_ratio, 
                    "human_cl" = clearance_type_by_er)
)
# Row, Columns
# In this case, rat is rows, human is columns
clearance_contingency_tbl <- table(combo_pretable$rat_cl, combo_pretable$human_cl)
addmargins(clearance_contingency_tbl)


```

I want to do some sensitivity analysis for hepatic blood flow.
The logic here is that, with nonrestrictive clearance, the clearance is
flow-dependent and therefore would be sensitive to increases in hepatic
blood flow. Restrictive compounds should not.  

For rats, the default hepatic blood flow (in mL/min/kg^(3/4)) is 33.38.
I will increase this by 1% (i.e. 0.3338) and look at the sensitivity of
steady-state concentration and total clearance.


```{r hbf_sensitivity}
# Find 1% increment
liver_tissue_new <- subset(tissue.data,
                           Tissue == "liver" &
                             Species == "Rat")

new_hepblfl_increment <- liver_tissue_new[
  liver_tissue_new$variable == "Flow (mL/min/kg^(3/4))",
  "value"
] * (1/100) # Get the increment amount (this is delta r)
# Calculate numerator for normalized sensitivity coefficient, 1%
drr <- new_hepblfl_increment/liver_tissue_new[
  liver_tissue_new$variable == "Flow (mL/min/kg^(3/4))",
  "value"
]

# Decrease "rest" of body blood flow
tissue.data[
  tissue.data$Tissue == "rest" &
    tissue.data$Species == "Rat" &
    tissue.data$variable == "Flow (mL/min/kg^(3/4))",
  "value"
  ] <- tissue.data[
  tissue.data$Tissue == "rest" &
    tissue.data$Species == "Rat" &
    tissue.data$variable == "Flow (mL/min/kg^(3/4))",
  "value"
  ] - new_hepblfl_increment
# Increase hepatic blood flow
tissue.data[
  tissue.data$Tissue == "liver" &
    tissue.data$Species == "Rat" &
    tissue.data$variable == "Flow (mL/min/kg^(3/4))",
  "value"
  ] <- 
  tissue.data[
  tissue.data$Tissue == "liver" &
    tissue.data$Species == "Rat" &
    tissue.data$variable == "Flow (mL/min/kg^(3/4))",
  "value"
  ] + new_hepblfl_increment
```

```{r}
# Next we need to re-parameterize the chemicals...
# I only need to do this under the assumption of restrictive clearance.
# The test is that under this assumption these chemicals should NOT be sensitive
# to the changes in hepatic blood flow.

rpr_sparams_rest <- tryCatch(
  expr = {
    sapply(
      target_chems_rat,
      \(x) {
        httk::parameterize_3comp2(
          dtxsid = x,
          species = "Rat",
          restrictive.clearance = TRUE,
          default.to.human = FALSE,
          force.human.clint.fup = FALSE,
          suppress.messages = TRUE
        )
      },
      simplify = FALSE,
      USE.NAMES = TRUE
    )
  }, error = function(msg) {
    message("Not possible to parameterize_3comp2 for all dtxsid ",
            "try to use default.to.human = TRUE.")
  }
)
# For these same chemicals, I also want to test sensitivity
# when parameterized as human for fup and Clint
rph_sparams_rest <- tryCatch(
  expr = {
    sapply(
      target_chems_rat,
      \(x) {
        httk::parameterize_3comp2(
          dtxsid = x,
          species = "Rat",
          restrictive.clearance = TRUE,
          default.to.human = TRUE,
          force.human.clint.fup = TRUE,
          suppress.messages = TRUE
        )
      },
      simplify = FALSE,
      USE.NAMES = TRUE
    )
  }, error = function(msg) {
    message("Not possible to parameterize_3comp2 for all dtxsid ",
            "try to use default.to.human = TRUE.")
  }
)


# Copied from RC_comparison_bkgd.R
css_httk_batch <- function(param_list,
                           restrictive = TRUE) {
  stopifnot(is.logical(restrictive))

  css_list_r <- vapply(
    param_list,
    \(x) {
      calc_analytic_css_3comp2(parameters = x,
                               restrictive.clearance = restrictive)
    },
    FUN.VALUE = numeric(1L)
  )
  css_list_names <- names(param_list)

  css_df <- data.frame(Chemical = css_list_names,
                       Css_httk_r.1p = css_list_r)
  return(css_df)
}

rpr_css_sensitivity <- css_httk_batch(rpr_sparams_rest)
rph_css_sensitivity <- css_httk_batch(rph_sparams_rest)

rpr_cltot_sensitivity <- data.frame(
      Chemical = names(rpr_sparams_rest),
      CLtot_restrictive.1p = vapply(
        rpr_sparams_rest,
        \(x) {
          httk::calc_total_clearance(
            parameters = x,
            species = "Rat",
            model = "3compartment2",
            suppress.messages = TRUE,
            restrictive.clearance = TRUE
          )
        },
        FUN.VALUE = double(1)
      ),
      halflife_restrictive.1p = vapply(
        rpr_sparams_rest,
        \(x) {
          httk::calc_half_life(
            parameters = x,
            species = "Rat",
            model = "3compartment2",
            suppress.messages = TRUE,
            restrictive.clearance = TRUE
          )
        },
        FUN.VALUE = double(1)
      )
)

rph_cltot_sensitivity <- data.frame(
      Chemical = names(rph_sparams_rest),
      CLtot_restrictive.1p = vapply(
        rph_sparams_rest,
        \(x) {
          httk::calc_total_clearance(
            parameters = x,
            species = "Rat",
            model = "3compartment2",
            suppress.messages = TRUE,
            restrictive.clearance = TRUE
          )
        },
        FUN.VALUE = double(1)
      ),
      halflife_restrictive.1p = vapply(
        rph_sparams_rest,
        \(x) {
          httk::calc_half_life(
            parameters = x,
            species = "Rat",
            model = "3compartment2",
            suppress.messages = TRUE,
            restrictive.clearance = TRUE
          )
        },
        FUN.VALUE = double(1)
      )
)

rpr_sensitivity <- merge(rpr_cltot_sensitivity,
                         rpr_css_sensitivity)

rph_sensitivity <- merge(rph_cltot_sensitivity,
                         rph_css_sensitivity)

rpr_sensitivity <- rpr_sensitivity %>%
  merge(rpr_httk_clearance_df) %>%
  mutate(
    nsc_css = ((Css_httk_r.1p - 
                  Css_httk_r)/Css_httk_r)/drr,
    nsc_cltot = ((CLtot_restrictive.1p -
                    CLtot_restrictive)/CLtot_restrictive)/drr,
    nsc_halflife = ((halflife_restrictive.1p -
                       halflife_restrictive)/halflife_restrictive)/drr
  ) %>%
  select(Chemical, Species, starts_with("nsc_"))

rph_sensitivity <- rph_sensitivity %>%
  merge(rpr_httk_clearance_df) %>%
  mutate(
    nsc_css = ((Css_httk_r.1p - 
                  Css_httk_r)/Css_httk_r)/drr,
    nsc_cltot = ((CLtot_restrictive.1p -
                    CLtot_restrictive)/CLtot_restrictive)/drr,
    nsc_halflife = ((halflife_restrictive.1p -
                       halflife_restrictive)/halflife_restrictive)/drr
  ) %>%
  select(Chemical, Species, starts_with("nsc_"))
  
rpr_sensitivity %>%
  mutate(across(starts_with("nsc_"),
                \(x) {
                  factor(
                    case_when(
                      abs(x) < 0.2 ~ 'Low',
                      between(abs(x), 0.2, 0.5) ~ 'Medium',
                      abs(x) > 0.5 ~ 'High'
                    ), levels = c('High', 'Medium', 'Low')
                  )
                })) %>% 
  count(nsc_css, nsc_cltot, nsc_halflife)

addmargins(clearance_contingency_tbl)

rph_sense_tables <- rph_sensitivity %>%
  mutate(across(starts_with("nsc_"),
                \(x) {
                  factor(
                    case_when(
                      abs(x) < 0.2 ~ 'Low',
                      between(abs(x), 0.2, 0.5) ~ 'Medium',
                      abs(x) > 0.5 ~ 'High'
                    ), levels = c('High', 'Medium', 'Low')
                  )
                })) %>%
  rename_with(\(x) {paste0(x, "_h")}, .cols = starts_with("nsc_"))

rpr_sense_tables <- rpr_sensitivity %>%
  mutate(across(starts_with("nsc_"),
                \(x) {
                  factor(
                    case_when(
                      abs(x) < 0.2 ~ 'Low',
                      between(abs(x), 0.2, 0.5) ~ 'Medium',
                      abs(x) > 0.5 ~ 'High'
                    ), levels = c('High', 'Medium', 'Low')
                  )
                })) %>% 
  left_join(combo_pretable) %>% 
  arrange(nsc_css, nsc_cltot, nsc_halflife) %>%
  relocate(rat_cl, human_cl, .after = Species) %>%
  mutate(
    cl = paste0("Rat:", rat_cl, "/Human:", human_cl),
  .keep = "unused", .after = Species) %>%
  left_join(rph_sense_tables) %>%
  left_join(fup_rh)

with(rpr_sense_tables,
     table(cl, nsc_halflife))

rpr_sense_tables %>%
  mutate(Rat_ambi = str_detect(cl, "Rat:Ambi")) %>%
  filter(!is.na(nsc_css)) %>%
  ggplot(aes(x = Clint_human, 
             y = Clint_rat, 
             color=cl)) +
  geom_point(alpha = 0.7, aes(shape = Rat_ambi)) +
  scale_shape_manual(values = c(16,21)) +
  scale_color_manual(
    values = c(
      "#d6604d", "red2", "#b2182b",
      "#fdb863", "#e08214", "#b35806",
      "#b2abd2", "#8073ac", "#542788")
  ) +
  labs(x = "Human", y = "Rat",
       title = "CL<sub>int</sub>",
       color = "Clearance Determination\nby Hepatic Extraction",
       shape = "Rat Clearance\ndetermined Ambiguous?") +
  facet_grid(rows = vars(nsc_halflife),
             scales = "free",
             space = "free_x") +
  geom_abline(slope = 1, color = "grey20") +
  theme_bw() +
  theme(plot.title = ggtext::element_markdown(hjust = 0.5))

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RestrictiveClearance_Analysis/",
                         "Rat_Human_Clint_Clearance_by_extractionRatio.png"),
       height = 7, width = 8,
       bg = "white")

```

Unfortunately, it seems that the sensitivity for Css, CLtot, and halflife
when parameterized with human fup and CLint values is quite high,
meaning they don't provide as much information as other metrics.


This next analysis looks at bootstrapping to look at specific variation in downstream
parameters (like Css and halflife) which depend on _kelim_ which cannot be estimated
at times. However, it is noted that even this method does not provide much more information.

```{r combination-function}
# Only need a simple bootstrapping method
combo_gen_splitter <- function(df, num = 1000L) {
  # Checks
  num = as.integer(num)
  stopifnot(
    is.data.frame(df),
    !is.na(num)
  )
  
  start <- 100L
  end <- 100L+num
  seed_seq <- seq.int(start, end)
  full_df_combos <- lapply(
    seed_seq,
    \(x) {
      set.seed(x)
      sample_df <- df %>%
        group_by(Chemical, Species, Reference, Route, Media, Dose, Time) %>%
        slice_sample(prop = 1, replace = TRUE) %>%
        ungroup()
      return(sample_df)
    }
  )
  
  
  message(paste("Samples: ", num))
  set.seed(NULL)
  invisible(full_df_combos)
}


```

```{r example_chemical}
# Using the example chemical
trial_coefsd <- coef_sd(full_pk)
trial_coefsd_reduced <- trial_coefsd %>% 
  filter(param_name %in% c("kelim", "Vdist", "V1")) %>%
  distinct()

trial_coefsd_reduced %>%
  filter(is.na(param_sd), model == "model_1comp") %>%
  distinct(Chemical, Species) -> selected_trial


test_chem_data <- get_data(full_pk) %>% filter(Conc > pLOQ) %>%
  count(Chemical, Species, Reference, Route, Media, Dose, Time) %>% arrange(-n) %>%
  filter(n > 4) %>%
  inner_join(selected_trial) %>%
  distinct(Chemical, Species, Reference, Route, Media, Dose) %>%
  inner_join(get_data(full_pk))

# Make 1000 sample data sets
system.time(
  test_chem_data_listsplits <- combo_gen_splitter(test_chem_data)
)

# Takes way too long, parallelize it

clust <- parallel::makeCluster(parallel::detectCores()-4L)
parallel::clusterCall(clust, function() devtools::load_all())
system.time(
  Css_list <- parallel::parLapply(
    clust,
    test_chem_data_listsplits,
    \(x) {
      tmp_pk <- pk(x,
                   mapping = ggplot2::aes(
                     Chemical = Chemical,
                     Chemical_Name = Chemical_Name,
                     DTXSID = DTXSID,
                     CASRN = CASRN,
                     Species = Species,
                     Reference = Reference,
                     Media = Media,
                     Route = Route,
                     Dose = Dose,
                     Dose.Units = "mg/kg",
                     Subject_ID = Subject_ID,
                     Series_ID = Series_ID,
                     Study_ID = Study_ID,
                     ConcTime_ID = ConcTime_ID,
                     N_Subjects = N_Subjects,
                     Weight = Weight,
                     Weight.Units = "kg",
                     Time = Time,
                     Time.Units = "hours",
                     Value = Value,
                     Value.Units = "mg/L",
                     Value_SD = Value_SD,
                     LOQ = LOQ
                   )
      ) +
        scale_conc(dose_norm = TRUE,
                   log10_trans = TRUE) +
        settings_optimx(method = c(
          "bobyqa"
        ))
      
      tmp_pk <- do_fit(tmp_pk)
      tmp_tkstats <- get_tkstats(tmp_pk) %>%
        distinct(Chemical, Species, Reference,
                 Route, Media,
                 model, method,
                 Css, CLtot, halflife)
      
      return(tmp_tkstats)
    })
)
parallel::stopCluster(clust)

Css_df_full <- bind_rows(Css_list)

```


```{r plotting-bootstraps}
num_samples <- length(Css_list)

test_chem_full_tkstats <- full_tkstats %>%
  filter(model != "model_flat") %>%
  inner_join(selected_trial) %>%
  distinct(Chemical, Species, model, Css)



Css_df_full %>%
  filter(model != "model_flat") %>%
  left_join(this_winmodel %>% 
              mutate(winmodel = TRUE) %>%
              select(-c(near_flat, preds_below_loq))) %>% 
  mutate(winmodel = ifelse(is.na(winmodel), FALSE, winmodel)) %>%
  ggplot(aes(x = halflife, y = Chemical, fill = winmodel)) +
  stat_slab() +
  # xlim(0,40) +
  scale_x_log10() +
  facet_grid(rows = vars(model),
             cols = vars(Route)) +
  scale_fill_manual(values = c("grey5", "green3")) +
  theme_bw() +
  labs(title = "halflife (hours)") +
  theme(
    axis.text.y = element_text(size = 6),
    axis.text.x = element_text(size = 10),
    plot.title = element_text(hjust = 0.5, size = 12),
    axis.title = element_blank()
  )
ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RestrictiveClearance_Analysis/",
                         "select_",
                         "halflife_bootstrapping.png"),
       bg = "white",
       height = 4, width = 6
)


css_hist <- Css_df_full %>%
  filter(model != "model_flat") %>%
  ggplot(aes(x = Css)) +
  geom_histogram(fill = "grey5", binwidth = 0.2) +
  geom_vline(data = test_chem_full_tkstats,
             aes(xintercept = Css),
             color = "green4",
             linetype = "dashed") +
  facet_grid(rows = vars(model)) +
  labs(title = unique(test_chem_data$Chemical_Name),
       subtitle = paste("Number of samples: ", num_samples)) +
  scale_x_log10() +
  xlim(0,50) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 1),
        plot.subtitle = element_text(hjust = 1))

css_lines <- Css_df_full %>%
  filter(model != "model_flat") %>%
  group_by(model) %>%
  mutate(grouping = row_number()) %>%
  ggplot(aes(x = model, y = Css)) +
  geom_point(alpha = 0.4) +
  geom_line(aes(group=grouping), alpha = 0.02) +
  scale_y_log10() +
  labs(subtitle = "N per timepoint: 4") +
  theme_bw()

get_winning_model(full_pk) %>% filter(Chemical == test_chem) %>% glimpse()

css_hist + css_lines

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RestrictiveClearance_Analysis/",
                         "CURRENT_", test_chem,
                         "_Css_pseudobootstrapping.png"),
       bg = "white",
       height = 3, width = 5
)
```



