---
title: "Restrictive Clearance Comparison"
author: "Gilberto Padilla Mercado"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This vignette describes comparisons between invivoPKfit predicted and those from httk.

```{r library_loading}
devtools::load_all()
library(httk)
library(tidyverse)
my_pk <- readRDS("data-raw/all_cvt_pk_JOINT.rds")
```


The first thing I need to do is get the chemicals included in both the CvTdb subset
and the httk empirical data for pbpk.

```{r chems_in_common}
common_chems <- cvt %>%
  subset(analyte_dtxsid %in% get_cheminfo(info = "DTXSID", model = "gas_pbtk")) %>%
  pull(analyte_dtxsid) %>%
  unique()

common_chems[!(common_chems %in% get_cheminfo(info = "DTXSID", model = "gas_pbtk"))] %>%
  unique() %>%
  sort()
```


```{r dawson}
# try dawson
httk::load_dawson2021()

common_chems_dawson <- cvt %>%
  subset(analyte_dtxsid %in% get_cheminfo(info = "DTXSID", model = "gas_pbtk")) %>%
  pull(analyte_dtxsid) %>%
  unique()


cvt %>%
  subset(!(analyte_dtxsid %in% get_cheminfo(info = "DTXSID", model = "gas_pbtk"))) %>%
  dplyr::distinct(analyte_dtxsid, analyte_name_original)

# Test which analyte_dtxsid don't have a clearance or vdist

data.frame(Chemical = unique(cvt$analyte_dtxsid)) %>%
  rowwise() %>%
  mutate(needs_RestCL = ifelse(
    (class(try(calc_total_clearance(dtxsid = Chemical,
                     restrictive.clearance = TRUE,
                     suppress.messages = TRUE))) == "try-error"),
    TRUE, FALSE),
    needs_nonRestCL = ifelse(
      (class(try(calc_total_clearance(dtxsid = Chemical,
                     restrictive.clearance = FALSE,
                     suppress.messages = TRUE))) == "try-error"),
    TRUE, FALSE),
    needs_Vdist = ifelse(
      (class(try(calc_vdist(dtxsid = Chemical,
                     suppress.messages = TRUE))) == "try-error"),
    TRUE, FALSE)) %>%
  ungroup() -> has_all_needed_df


has_all_needed_df %>%
  filter(!(needs_RestCL | needs_nonRestCL | needs_Vdist)) %>%
  pull(Chemical) %>% unique() -> common_chems_dawson

```

Next I need to get the clearances using the `calc_total_clearance(dtxsid, restrictive.clearance)`
function from httk. Also need the clearances from invivoPKfit's winning models.


```{r get_clearances}
clearance_df <- data.frame(Chemical = common_chems) %>%
  rowwise() %>%
  mutate(Restrict_Cl = calc_total_clearance(dtxsid = Chemical,
                                            restrictive.clearance = TRUE,
                                            suppress.messages = TRUE),
         nonRestrict_Cl = calc_total_clearance(dtxsid = Chemical,
                                            restrictive.clearance = FALSE,
                                            suppress.messages = TRUE)) %>%
  ungroup()

hep_clearance_df <- data.frame(Chemical = common_chems) %>%
  rowwise() %>%
  mutate(Restrict_Cl = calc_hep_clearance(dtxsid = Chemical,
                                            restrictive.clearance = TRUE,
                                            suppress.messages = TRUE),
         nonRestrict_Cl = calc_hep_clearance(dtxsid = Chemical,
                                            restrictive.clearance = FALSE,
                                            suppress.messages = TRUE)) %>%
  ungroup()

my_tkstats <- eval_tkstats(my_pk) %>%
  dplyr::select(Chemical, Species, CLtot.tkstats, CLtot.nca) %>%
  distinct() %>%
  filter(Chemical %in% common_chems,
         !is.na(CLtot.tkstats), !is.na(CLtot.nca)) %>%
  group_by(Chemical, Species, CLtot.tkstats) %>%
  summarize(CLtot.nca_mean = mean(CLtot.nca),
            CLtot.nca_sd = sd(CLtot.nca))

# Combine these two
combined_clearance_df <- my_tkstats %>% inner_join(clearance_df)

```


Finally, let's visualize where the tkstats predictions land.

```{r viz}

# Preliminary viz, plot all clearances
combined_clearance_df %>%
  relocate(CLtot.nca_mean, CLtot.nca_sd, .after = tidyselect::last_col()) %>%
  pivot_longer(cols = 3:6,
               names_to = "Clearance_Source",
               values_to = "Value") %>%
  ggplot(aes(x = Value,
             y = Chemical,
             fill = Clearance_Source)) +
  geom_point(shape = 21, alpha = 0.7) +
  scale_x_log10() +
  scale_fill_manual(breaks = c("nonRestrict_Cl", "CLtot.tkstats",
                               "CLtot.nca_mean",
                               "Restrict_Cl"),
                    labels = c("non-restrictive clearance (httk)",
                               "predicted clearance (invivoPKfit)",
                               "mean non-compartmental total clearance (invivoPKfit)",
                               "restrictive clearance (httk)"),
                    values = c("orange2", "grey5", "skyblue3",  "green4")) +
  facet_grid(rows = vars(Species), scales = "free", space = "free") +
  theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face = "bold"),
        legend.position = "bottom",
        legend.direction = "vertical",
        axis.ticks = element_blank(),
        axis.line = element_blank())


ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "tkClearance_comparison_httk_gasPBPK.png"),
       height = 14,
       width = 5,
       device = "png")
```

Finally, what I want to analyze is how good the fits for these chemicals are relative to the rest of the chemicals.

```{r fit_analysis}
wm <- get_winning_model(my_pk)
ingroup_rmse <- rsq(my_pk) %>% inner_join(wm) %>%
  filter(Chemical %in% combined_clearance_df$Chemical) %>%
  mutate(Group = "in httk")

outgroup_rmse <- rsq(my_pk) %>% inner_join(wm) %>%
  filter(!(Chemical %in% combined_clearance_df$Chemical)) %>%
  mutate(Group = "not in httk")

all_group_rmse <- bind_rows(ingroup_rmse, outgroup_rmse)


all_group_rmse %>%
  filter(Species == "rat") %>%
  ggplot(aes(x = Rsq, y = Chemical,
             shape = Group)) +
  geom_point() +
  facet_grid(rows = vars(Group), scales = "free", space = "free") +
  theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face = "bold"),
        legend.direction = "vertical",
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        axis.text.y = element_blank())

ggsave(paste0(Sys.getenv("FIG_DIR"), "Rsq_gaspbtk.png"),
       height = 5,
       width = 5)
  

```

## Exploring _httk_ parameters and solved values for `gas_pbtk`

```{r httk_solution}
httk::calc_tkstats(dtxsid = unique(combined_clearance_df$Chemical)[[5]])
httk::parameterize_gas_pbtk(restrictive.clearance = TRUE,
                            dtxsid = unique(combined_clearance_df$Chemical)[[5]])

httk::solve_gas_pbtk(dtxsid = unique(combined_clearance_df$Chemical)[[5]],
                     parameters = httk::parameterize_gas_pbtk(
                       restrictive.clearance = TRUE,
                       dtxsid = unique(combined_clearance_df$Chemical)[[5]]
                       ),
                     dose = 10,
                     exp.conc = 0,
                     input.units = "mg",
                     output.units = "mg",
                     days = 3,
                     plots = TRUE)


# For the invivoPKfit functions, we will hold kelim constant
# This constant will be calculated as CLtot/Vdist (or V1, if 2-compartment)
# This constant is derived by httk in the following way:
calc_total_clearance(dtxsid = common_chems[[10]],
                             restrictive.clearance = FALSE) /
  calc_vdist(dtxsid = common_chems[[10]])

```

I have modified the starts of the 1- and 2-compartment models,
as well as adding a restrictive_clearance argument in stat_model.

```{r running-invivoPKfit}
# This is now updated to use dawson chem table
minimal_pk <- pk(data = cvt %>%
                   filter(analyte_dtxsid %in% common_chems_dawson),
                 mapping = ggplot2::aes(
                   Chemical = analyte_dtxsid,
                   Chemical_Name = analyte_name_original,
                   DTXSID = analyte_dtxsid,
                   CASRN = analyte_casrn,
                   Species = species,
                   Reference = document_id,
                   Media = conc_medium_normalized,
                   Route = administration_route_normalized,
                   Dose = dose_level_normalized,
                   Dose.Units = "mg/kg",
                   Subject_ID = subject_id,
                   Series_ID = series_id,
                   Study_ID = study_id,
                   ConcTime_ID = conc_time_id,
                   N_Subjects = n_subjects_in_series,
                   Weight = weight_kg,
                   Weight.Units = "kg",
                   Time = time_hr,
                   Time.Units = "hours",
                   Value = conc,
                   Value.Units = "mg/L",
                   Value_SD = conc_sd_normalized,
                   LOQ = loq
                 ))


new_pk <- minimal_pk +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c("L-BFGS-B")) +
  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
  stat_error_model(error_group = vars(Chemical, Species, Reference)) +
  stat_model(model = c("model_1comp", "model_1comp_cl_rest", "model_1comp_cl_nonrest"))
new_pk <- do_data_info(new_pk)


new_pk <- do_prefit(new_pk)

new_pk$prefit$par_DF %>% arrange(Chemical, Species) %>% filter(param_name == "Clint") %>%
  View()

new_pk <- do_fit(new_pk) # For troubleshooting only



new_pk <- do_fit(new_pk, n_cores = 12)


# Multidplyr error because of forgotten browser() call within log_likelihood
new_pk$fit %>% unnest(fit) %>% View()

saveRDS(new_pk, "data-raw/someCVT_wHTTK_JOINT.rds")


coef(new_pk) %>% View()
eval_tkstats(new_pk, finite_only = FALSE) %>% View()
get_winning_model(new_pk) %>% View("winning_model")


AIC(new_pk) %>% filter(method %in% "L-BFGS-B") %>% arrange(Chemical, Species) %>%
  View()

pl2comp <- plot(new_pk, use_scale_conc = FALSE,
           # model = "model_2comp_nonrest",
           n_interp = 10)


pl2comp %>%
  filter(Chemical %in% "DTXSID1043881") %>% pull(final_plot) %>% .[[1]]
```


Why are so many fits failing?
Well, we should take a look at the parameter which we are holding constant,
`kelim` and whether the new starting points vastly differ from those in the
starting points based on the data.

For this I will just use the PK object I have saved `my_pk` and take the
_prefit_ parameter estimations and first compare that with eventual optimized `kelim`.

```{r kelim-questions}

# Original data, filtered for common_chems
# par_DF
my_kelim_prefit <- my_pk$prefit$par_DF %>%
  filter(param_name %in% "kelim",
         Chemical %in% common_chems) %>%
  distinct(Chemical, Species, param_name, lower_bound, upper_bound, start)

my_kelim_fit <- coef(my_pk) %>%
  inner_join(get_winning_model(my_pk)) %>%
  ungroup() %>%
  distinct(model, Chemical, Species, kelim) %>%
  rename(fit_kelim = "kelim") %>%
  filter(Chemical %in% common_chems)

my_kelim_df <- inner_join(my_kelim_fit, my_kelim_prefit)


httk_df <- rest_pk$prefit$par_DF %>%
  filter(param_name %in% "kelim") %>%
  distinct(Chemical, Species, param_name, start) %>%
  rename(init_restrictive = "start") %>%
  inner_join(
    nonrest_pk$prefit$par_DF %>%
  filter(param_name %in% "kelim") %>%
  distinct(Chemical, Species, param_name, start) %>%
  rename(init_nonrestrictive = "start"))


full_df <- inner_join(my_kelim_df, httk_df) %>%
  relocate(fit_kelim, .after = last_col())


full_df %>%
  ggplot(aes(x = Chemical)) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "grey30") +
  geom_errorbar(aes(ymax = upper_bound, ymin = lower_bound)) +
  geom_point(aes(y = fit_kelim, color = "Original Optimized")) +
  geom_point(aes(y = init_restrictive, color = "Restrictive")) +
  geom_point(aes(y = init_nonrestrictive, color = "Non-restrictive")) +
  geom_point(aes(y = start, shape = "Original Initialized")) +
  facet_grid(rows = vars(Species), scales = "free", space = "free") +
  scale_color_manual(name = "kelim",
                     breaks = c("Original Optimized", "Restrictive", "Non-restrictive"),
                     values = c("Original Optimized" = "skyblue4", 
                                "Restrictive" = "orange2",
                                "Non-restrictive" = "green4")) +
  scale_shape_manual(name = "",
                     values = 4) +
  coord_flip() +
  scale_y_log10(labels = scales::label_math(format = log10)) +
  theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face = "bold"),
        legend.direction = "vertical",
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        axis.text.y = element_blank(),
        strip.text.y = element_text(angle = 0))


ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "kelim_compare_2024_0329.png"),
       height = 11,
       width = 8.5)


```



```{r new_analysis}
# Loading the new data
new_pk <- readRDS("data-raw/someCVT_wHTTK_JOINT.rds")

new_wm <- get_winning_model(new_pk)
new_AIC <- AIC(new_pk)
new_rsq <- rsq(new_pk)
new_rmse <- rmse(new_pk, use_scale_conc = FALSE)

new_tkstats <- eval_tkstats(new_pk, finite_only = FALSE)


new_resid <- residuals(new_pk)

my_data <- get_data(new_pk) %>%
  distinct(Chemical, Species, Reference, Route, Media, Dose, Time, Conc) %>%
  right_join(new_resid)


pl <- plot(new_pk, n_interp = 12, use_scale_conc = FALSE)
pdf(file = paste0(Sys.getenv("FIG_DIR"),
              "AllFits_nonDoseNorm_newPK_reParametizedModels_2024_0412.pdf"),
    height = 6, width = 10)
for (i in 1:nrow(pl)) {
  print(pl$final_plot[[i]])
}
dev.off()


```

Comparing total clearance estimates for those where a restrictive or non-restrictive model
was the "best fit" as determined by AIC.

```{r cltot-comparison}
new_cltot2 <- new_tkstats %>% 
  filter(str_detect(model, "rest")) %>%
  select(Chemical, Species, Media, Route, 
         model, method,
         CLtot.tkstats, CLtot.nca) %>%
  filter(!is.na(CLtot.tkstats)) %>%
  mutate(clearance_type = ifelse(str_detect(model, "nonrest"),
                                "NonRestrictive",
                                ifelse(str_detect(model, "rest"),
                                       "Restrictive",
                                       "optimized kelim"))) %>%
  rowwise() %>%
  mutate(CLtot.httk_rest = calc_total_clearance(dtxsid = Chemical,
                                           restrictive.clearance = TRUE),
         CLtot.httk_nonrest = calc_total_clearance(dtxsid = Chemical,
                                           restrictive.clearance = FALSE))



new_cltot2 %>%
  ggplot(aes(x = Chemical)) +
  geom_point(aes(y = CLtot.httk_rest),shape = 19, size = 2, color = "green4") +
  geom_point(aes(y = CLtot.httk_nonrest),shape = 19, size = 2, color = "orange2") +
  geom_point(aes(y = CLtot.tkstats, shape = Species), size = 3, color = "black", stroke = 1) +
  scale_y_log10(labels = scales::label_math(format = log10)) +
  geom_hline(yintercept = c(0.01, 0.1, 1, 10)) +
  scale_shape_manual(values = c(0,1,2,5,6)) +
  coord_flip() +
  facet_grid(rows = vars(clearance_type),
             scales = "free", space = "free") +
  labs(title = "CLtot for constant kelim \"best fits\" (empty)\nand httk calculations (filled)") +
  theme_bw() +
  theme(axis.line = element_line(linewidth = 1),
        axis.text = element_text(size = 12),
        axis.title = element_blank(),
        plot.title = element_text(hjust = 0.5),
        plot.background = element_rect(fill = "white"),
        strip.text.y = element_text(angle = 0),
        strip.background = element_blank(),
        legend.position = "none")

ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "Cltot_backcompare_wDawson_2024_0416.png"),
       height = 8,
       width = 9)


```

```{r chemical-correlation}
new_AIC %>%
  ungroup() %>%
  filter(model %in% c("model_1comp", "model_2comp"),
         Species %in% "rat") %>%
  group_by(Chemical) %>%
  filter(AIC == min(AIC)) %>%
  mutate(estimate = "nonConst") %>%
  distinct(Chemical, model, estimate) -> nAIC_nonConst
new_AIC %>%
  ungroup() %>%
  filter(model %in% c("model_1comp_rest", "model_2comp_rest"),
         Species %in% "rat") %>%
  group_by(Chemical) %>%
  filter(AIC == min(AIC)) %>%
  mutate(estimate = "Rest") %>%
  distinct(Chemical, model, estimate) -> nAIC_rest
new_AIC %>%
  ungroup() %>%
  filter(model %in% c("model_1comp_nonrest", "model_2comp_nonrest"),
         Species %in% "rat") %>%
  group_by(Chemical) %>%
  filter(AIC == min(AIC)) %>%
  mutate(estimate = "nonRest") %>%
  distinct(Chemical, model, estimate) -> nAIC_nonrest

full_nAIC <- bind_rows(nAIC_nonConst, nAIC_rest) %>%
  bind_rows(nAIC_nonrest)

new_tkstats_full <- get_tkstats(new_pk)

new_tkstats_full %>%
  filter(Species %in% "rat", !(model %in% "model_flat")) %>%
  distinct(Chemical, model, CLtot) %>%
  inner_join(full_nAIC) %>%
  na.omit() %>% 
  distinct(Chemical, estimate, CLtot) %>%
  pivot_wider(names_from = estimate,
              values_from = CLtot) %>%
  rowwise() %>%
  mutate(CLtot.httk_rest = calc_total_clearance(dtxsid = Chemical,
                                           restrictive.clearance = TRUE),
         CLtot.httk_nonrest = calc_total_clearance(dtxsid = Chemical,
                                           restrictive.clearance = FALSE)) %>%
  ungroup() %>%
  mutate(A_rest = log(nonConst) - log(CLtot.httk_rest),
         A_nonrest = log(nonConst) - log(CLtot.httk_nonrest),
         B_rest = log(Rest) - log(CLtot.httk_rest),
         B_nonrest = log(Rest) - log(CLtot.httk_nonrest),
         C_rest = log(nonRest) - log(CLtot.httk_rest),
         C_nonrest = log(nonRest) - log(CLtot.httk_nonrest)) %>%
  select(Chemical, A_rest:C_nonrest) -> df_valcomp

df_valcomp %>% 
  column_to_rownames(var = "Chemical") %>%
  t() %>%
  as.matrix() %>%
  cor() %>%
  signif() -> val_cormat

hclust(d = as.dist((1+val_cormat)/2), method = "average") %>% plot()

hclust(d = as.dist((1+val_cormat)/2), method = "average") -> val_hclust

corrplot::corrplot(abs(val_cormat))

#reorder the Chemical names prior to plotting
df_valcomp %>%
  mutate(Chemical = factor(x = Chemical,
                           levels = val_hclust$labels[val_hclust$order])) %>%
  pivot_longer(cols = A_rest:C_nonrest,
               names_to = "comparison", values_to = "logres") %>%
  mutate(comparison = case_when(
    comparison == "A_nonrest" ~ "free kelim vs httk nonrestrictive",
    comparison == "A_rest" ~ "free kelim vs httk restrictive",
    comparison == "B_nonrest" ~ "restrictive kelim vs httk nonrestrictive",
    comparison == "B_rest" ~ "restrictive kelim vs httk restrictive",
    comparison == "C_nonrest" ~ "nonrestrictive kelim vs httk nonrestrictive",
    comparison == "C_rest" ~ "nonrestrictive kelim vs httk restrictive",
  ),
  comparison = factor(comparison,
  levels = c("free kelim vs httk restrictive",
             "free kelim vs httk nonrestrictive",
             "restrictive kelim vs httk restrictive",
             "nonrestrictive kelim vs httk nonrestrictive",
             "nonrestrictive kelim vs httk restrictive",
             "restrictive kelim vs httk nonrestrictive"))) %>%
  ggplot(aes(x = comparison, y = Chemical, fill = logres)) +
  geom_tile() +
  scale_fill_gradient2(mid = "grey5", high = "orange", low = "green3",
                       name = "Total Clearance\nlog10-scale difference",
                       limits = c(-4, 4),
                       oob = scales::oob_squish) +
  coord_fixed(ratio = 0.3) +
  theme_bw() +
  theme(axis.text.x = element_text(hjust = 1, angle = 45),
        axis.ticks.y = element_blank(),
        panel.grid = element_blank(),
        axis.title.x = element_blank())

ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "Cltot_compare_heatmap_2024_0409.png"),
       height = 14,
       width = 8)

```

# Winning models - An aside

I am a little worried that I am not selecting the best fit model for each
chemical all the time. Ultimately, the consequences for this being having parameters
for chemicals with rather poor fits in general, when there is a better fitting
model available. Here I want to do a quick analysis of the chemical
*DTXSID3022405* in mouse. The one compartment fits best in the original data
(by visual inspection) but the 2-compartment wins out in minimizing AIC.

For each model, I can find how many distinct experimental timepoints have the minimum
RMSE then investigate whether the model with the most _minimum RMSE_ timepoint
corresponds to the winning model by AIC.

*Update*: About half do not correspond. However, the lack of correspondance doesn't
mean there is bad fits declared winning model. To address this I need to understand 
_how_ different the AIC-based winning model and the RMSE-based winning models
are and whether the data leaves something to be desired.
This may be as simple as a Pearson correlation between residual values.
The output of this analysis is how related both

Another thing I am noticing in oral data: the constant _kelim_ fits sometimes are very similar
to their respective non-constant _kelim_ fits and they actually intersect/cross over.
I wonder if there is something special about the timepoints at which they intersect.
For example, a restrictive fit will reach a slightly higher Cmax, but then
dive below the fully optimized fit during elimination phase before crossing over
again near the second inflection point.

```{r oxybenzene-test}
old_AIC <- AIC(my_pk) %>%
  filter(Chemical %in% "DTXSID3022405",
         Species %in% "mouse")

new_AIC <- new_AIC %>%
  filter(Chemical %in% "DTXSID3022405",
         Species %in% "mouse")

plot(new_pk, model = c("model_2comp",
                       "model_1comp", "model_1comp_nonrest"),
     use_scale_conc = FALSE) %>%
  filter(Chemical %in% "DTXSID3022405",
         Species %in% "mouse") %>%
  pull(final_plot) %>% .[[1]]

old_rsquared <- rmse(my_pk) %>%
  filter(Chemical %in% "DTXSID3022405",
         Species %in% "mouse")

# Only test residual correlations with those not the same

winmodel_conflict <- rmse(new_pk, use_scale_conc = FALSE) %>%
  group_by(Chemical, Species, Route, Media, Dose, Time) %>%
  filter(RMSE == min(RMSE)) %>%
  group_by(Chemical, Species) %>%
  count(model) %>%
  filter(n == max(n)) %>%
  inner_join(new_wm %>% rename("winmodel" = "model")) %>%
  filter(!(model == winmodel))

# need to map2 then have `residuals.pk(model = .x)` and .y
# then correlate these values for each data group
winmodel_conflict %>% names()

mod_red <- winmodel_conflict %>%
  dplyr::select(Chemical, Species, model) %>%
  left_join(new_resid,
            by = join_by(Chemical, Species, model)) %>%
  rename("mod_residuals" = "Residuals") %>%
  select(Chemical, Species, Route, Media, Time, Detect, exclude,
         model, mod_residuals)

wm_red <- winmodel_conflict %>%
  dplyr::select(Chemical, Species, winmodel) %>%
  left_join(new_resid,
            by = join_by(Chemical, Species, "winmodel" == "model")) %>%
  rename("wm_residuals" = "Residuals") %>%
  select(Chemical, Species, Route, Media, Time, Detect, exclude,
         winmodel, wm_residuals)
sum_red <- new_resid %>%
  group_by(Chemical, Species, model) %>%
  summarize(MSE = sum(Residuals^2)/n())


cor_mod <- mod_red %>% inner_join(wm_red) %>%
  select(Chemical, Species, model, mod_residuals, winmodel, wm_residuals) %>%
  group_by(Chemical, Species, model, winmodel) %>%
  summarize(cor_mods = cor(x = mod_residuals, y = wm_residuals)) %>%
  left_join(sum_red, by = join_by(Chemical, Species, model)) %>%
  rename("mod_MSE" = "MSE") %>%
  left_join(sum_red, by = join_by(Chemical, Species, "winmodel" == "model")) %>%
  rename("wm_MSE" = "MSE")


my_pl_1comp <- plot(new_pk, n_interp = 11, use_scale_conc = FALSE,
                    model = c("model_1comp",
                              "model_1comp_rest",
                              "model_1comp_nonrest"))

my_pl_2comp <- plot(new_pk, n_interp = 11, use_scale_conc = FALSE,
                    model = c("model_2comp",
                              "model_2comp_rest",
                              "model_2comp_nonrest"))


# General trends about residual correlation and MSE
cor_mod %>%
  mutate(cor_bin = ifelse(abs(cor_mods) >= 0.60,
                          "Taking win_model",
                          "Taking low RMSE model")) %>% na.omit() %>%
  ggplot() +
  geom_point(aes(x = mod_MSE, y = wm_MSE)) +
  scale_x_log10() +
  scale_y_log10() +
  geom_abline(slope = 1, intercept = 0, linetype = "dotted") +
  facet_grid(rows = vars(cor_bin))


cor_mod %>%
  filter(!(model %in% "model_flat")) %>%
  mutate(cor_bin = ifelse(abs(cor_mods) >= 0.60,
                          "Taking win_model",
                          "Taking low RMSE model")) %>% na.omit() %>%
  ggplot() +
  geom_histogram(aes(x = cor_mods, fill = model),
                 binwidth = 0.05) +
  facet_grid(rows = vars(winmodel)) +
  scale_fill_viridis_d() +
  theme_bw() +
  theme(strip.text.y = element_text(angle = 0)) +
  labs(x = "Correlation of Residuals",
       fill = "model by grouped RMSE")

ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "winModel_correlations_changes",
                         "_2024_Apr_16.png"),
       height = 6,
       width = 8)

# Try oxybenzone fitting without dose-norm
minimal_pk <- pk(data = cvt %>%
                   filter(analyte_dtxsid %in% "DTXSID3022405"),
                 mapping = ggplot2::aes(
                   Chemical = analyte_dtxsid,
                   Chemical_Name = analyte_name_original,
                   DTXSID = analyte_dtxsid,
                   CASRN = analyte_casrn,
                   Species = species,
                   Reference = document_id,
                   Media = conc_medium_normalized,
                   Route = administration_route_normalized,
                   Dose = dose_level_normalized,
                   Dose.Units = "mg/kg",
                   Subject_ID = subject_id,
                   Series_ID = series_id,
                   Study_ID = study_id,
                   ConcTime_ID = conc_time_id,
                   N_Subjects = n_subjects_in_series,
                   Weight = weight_kg,
                   Weight.Units = "kg",
                   Time = time_hr,
                   Time.Units = "hours",
                   Value = conc,
                   Value.Units = "mg/L",
                   Value_SD = conc_sd_normalized,
                   LOQ = loq
                 ))
new_pk <- minimal_pk +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c("L-BFGS-B")) +
  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
  stat_error_model(error_group = vars(Chemical, Species, Reference)) +
  stat_model(model = c("model_flat", "model_1comp", "model_2comp",
                       "model_1comp_rest", "model_1comp_nonrest",
                       "model_2comp_rest", "model_2comp_nonrest"))

new_pk <- do_fit(new_pk, n_cores = 3) 
get_winning_model(new_pk)
plot(new_pk, best_fit = TRUE) %>% pull(final_plot)
```




# Categorizing chemicals

I first need to find the winning model for constant kelims and optimized kelims

```{r categorization}

grouped_wm <- new_AIC %>%
  mutate(model_type = case_when(
    str_detect(model, "_nonrest$") ~ "Nonrestrictive",
    str_detect(model, "_rest$") ~ "Restrictive",
    .default = "Free_kelim"
  )) %>%
  group_by(Chemical, Species, model_type) %>%
  filter(AIC == min(AIC)) %>% 
  ungroup() %>%
  arrange(Chemical, Species, model_type) %>%
  select(Chemical, Species, model, method, model_type)


grouped_tkstats <- get_tkstats(new_pk) %>%
  inner_join(grouped_wm)

grouped_tkstats %>%
  select(Chemical, Species, Reference,
         Route, Media, model_type,
         CLtot) %>%
  pivot_wider(names_from = model_type, values_from = CLtot) %>%
  mutate(low_invivo_CL = ifelse(
    Free_kelim < Nonrestrictive/2 | Free_kelim < Restrictive/2,
    TRUE, FALSE),
    high_extra_hepCL = ifelse(
      Free_kelim > 1.5*Nonrestrictive | Free_kelim > 1.5*Restrictive,
      TRUE, FALSE),
    rest_metabol = ifelse(
      Free_kelim > Restrictive/2 & Free_kelim < 1.5*Nonrestrictive,
      TRUE, FALSE),
    combo_cat = paste0(low_invivo_CL + 0,
                       high_extra_hepCL + 0,
                       rest_metabol + 0)) %>%
  count(combo_cat)
  arrange(Chemical, combo_cat) %>%
  na.omit() %>%
  View()

```



```{r}
my_tkstats <- eval_tkstats(my_pk, finite_only = FALSE)

my_tkstats %>% filter(Species %in% "rat",
                      Route %in% "oral") %>%
  distinct(Chemical, Species, Route, Media, model, Fgutabs.tkstats) %>%
  filter(Fgutabs.tkstats > 0) %>%
  left_join(distinct(cas_convert)) %>% 
  arrange(Chemical) %>% clipr::write_clip()


pesticides <- read_csv("C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Chemical List EPAPCS-2024-04-17.csv") %>%
  pull(DTXSID) %>% str_extract("DTXSID\\d+")


unique(my_tkstats$Chemical)[unique(my_tkstats$Chemical) %in% pesticides]


```

## New reformulated models that estimate Clint!

```{r reformMod}
new_pk$fit %>% unnest(fit) %>%
  mutate(Clint = ifelse(model == "model_1comp", kelim/Vdist, Clint)) %>%
  select(Chemical, Species, model, Clint) %>%
  pivot_wider(names_from = model, values_from = Clint) %>%
  left_join(new_pk$prefit$par_DF %>%
              filter(param_name == "Clint") %>%
              select(Chemical, Species, model, start) %>%
              mutate(model = paste0("start_", model)) %>%
              pivot_wider(names_from = model,
                          values_from = start)) %>% View()


get_tkstats(new_pk)


```



