---
title: "Plot curve fits"
author: "Caroline Ring"
date: "2023-01-04"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(results = TRUE)
knitr::opts_chunk$set(message = FALSE)
```

```{r, include = FALSE}
library(tidyverse)
library(data.table)
library(readxl)
devtools::load_all("../invivopkfit")
```

Read in CvTdb data pulled in `pulling_oral_iv_data_cvtdb.Rmd`.

```{r, load_cvt, eval = TRUE}
cvt_data <- fread("../inst/ext/cvt_data_2023_01_05_09_37_22.csv")
```

For ease of plotting, get the pre-processed, harmonized data:

```{r}
cvt <- preprocess_data(data.set = cvt_data,
                       names_list =list(
                         "Compound_Dosed" = "studies.test_substance_name_original",
                         "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
                         "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
                         "Compound_Analyzed" = "series.analyte_name_original",
                         "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
                         "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
                         "Reference" = "documents_reference.id",
                         "Extraction" = "documents_extraction.id",
                         "Species" = "subjects.species",
                         "Weight" ="subjects.weight_kg",
                         "Weight.Units" = NULL,
                         "Dose" = "studies.dose_level_normalized_corrected", #note that dose levels were corrected in pulling_oral_iv_data_cvtdb.Rmd
                         "Dose.Units" = NULL,
                         "Time" = "conc_time_values.time_hr",
                         "Time.Units" = NULL,
                         "Media" = "series.conc_medium_normalized",
                         "Value" = "conc_time_values.conc", #already in mg/L units
                         "Value.Units" = NULL,
                         "Route" = "studies.administration_route_normalized",
                         "LOQ" = "series.loq_normalized", #note that LOQs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
                         "Subject" = "subjects.id",
                         "N_Subjects" = "series.n_subjects_in_series",
                         "Value_SD" = "conc_time_values.conc_sd_normalized" #note that SDs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
                         ),
                       defaults_list =   list(
                         "Weight.Units" = "kg",
                         "Dose.Units" = "mg/kg",
                         "Time.Units" = "h",
                         "Value.Units" = "mg/L"),
                       ratio_conc_to_dose = 1,
                       calc_loq_factor = 0.45,
                       routes_keep = c("po", "iv"),
                       media_keep = c("blood", "plasma"),
                       suppress.messages = FALSE)
cvt <- as.data.table(cvt)
```

Read in the fitted model parameter values.

```{r, read_data}
timestamp <- "2023_01_04_10_56"
PK.fit.table.1comp <- fread(paste0("../inst/ext/", "PK_fit_table_1comp_", timestamp, ".csv",sep=""))
PK.fit.table.2comp <- fread(paste0("../inst/ext/", "PK_fit_table_2comp_", timestamp, ".csv",sep=""))
PK.fit.table.flat <- fread(paste0("../inst/ext/", "PK_fit_table_flat_", timestamp, ".csv",sep=""))

#pk_lombardo <- read_xlsx("inst/ext/Supplemental_82966_revised_corrected.xlsx")
```

Rowbind together all of the fitted parameter tables into one big one.
```{r}
pk_fit <- rbindlist(list("1comp" = PK.fit.table.1comp,
                         "2comp" = PK.fit.table.2comp,
                         "flat" = PK.fit.table.flat),
                    use.names = TRUE,
                    fill = TRUE)
```


Get a table of the winning model for each dataset (the one with minimum AIC).

```{r}
tmp <- unique(pk_fit[, .(DTXSID, Species, Analysis_Type, References.Analyzed, model, AIC)])

#sort AIC from smallest to largest within each dataset, putting NAs last
setorder(tmp, DTXSID, Species, Analysis_Type, References.Analyzed, AIC, na.last = TRUE)
#the winning model will now be listed first within each dataset (smallest AIC)
model_win <- tmp[, .(winmodel = model[1]), by = .(DTXSID, Species, Analysis_Type, References.Analyzed)]
pk_fit <- model_win[pk_fit, on = c("DTXSID", "Species", "Analysis_Type", "References.Analyzed")]
pk_fit[, winning:=(model == winmodel)]

```

Plot concentration vs time with the best-fit params by data subset (DTXSID and species). 

Indicate the following:

- One line for each model
- Which is the winning model
- Dose group
- Blood vs. plasma
- Below LOQ vs. above LOQ (plot below-LOQ points at LOQ)
- IV vs. oral administration


Would also like to plot uncertainty in predictions based on uncertainty in parameter estimates.

Plot versions:
- Winning model only
- One model at a time
- All three models on same plot

Get unique combinations of DTXSID and species -- each of these will be one plot.

```{r}
plot_table <- unique(pk_fit[, .(DTXSID, Species)])
```

Plot all models for the joint analysis.
```{r}

#plot all models
tmp <- mapply(plot_fit,
              DTXSID_in = plot_table$DTXSID,
                     Species_in = plot_table$Species,
              MoreArgs = list(
                     model_in = "all",
                     Analysis_Type_in = "Joint",
                     DF = cvt,
                     pk_fit = pk_fit,
                     n = 101,
                     limit_y_axis = FALSE,
                     log10_scale_y = FALSE,
                     plot_errbars = TRUE,
                     log10_scale_time = FALSE,
                     file_path = "../inst/ext/plots/Joint Analysis/model_all/")
                     )

```

Problem: DTXSID0022985_rat_Joint_all does not plot any model lines. Why?

```{r}
pk_fit[DTXSID %in% "DTXSID0022985"]
```

Apparently there were no detected data points?

```{r}
cvt[DTXSID %in% "DTXSID0022985", .(Reference, Value, LOQ)]
```

Hmm. Something is very weird here. I definitely see some detected points. They are all the same reference, so it isn't that a single-reference fit did not work but a joint fit did work. 

Plot only the winning model

```{r}
#plot all models
tmp <- mapply(plot_fit,
              DTXSID_in = plot_table$DTXSID,
                     Species_in = plot_table$Species,
              MoreArgs = list(
                Analysis_Type_in = c("Joint", "Separate"),
                     model_in = "winning",
                     fitdata = DF,
                     pk_fit = pk_fit,
                     file_path = "inst/ext/plots/analysis_all_model_winning/",
                log10_scale_time = TRUE)
                     )
```


